\section{Introduction}
\subsection{Problem Statement}
Bridging the gap between virtual and real worlds, Augmented Reality (AR) provides new possibilities of teaching and learning which have been increasingly recognized by educational reaserchers. \autocite [cf.][41]{Wu.2013} Although AR is one of the most emerging technologies in education in these days \autocite [cf.][]{Johnson.2010}, the unique value of AR learning environments remains unclear. \autocite [cf.][48]{Wu.2013} In addition, there are different types of AR applications in educational environments which may differ regarding their benefits towards educational outcomes. \autocite [cf.][127-130]{Yuen.2011} This leads to the problem that teachers and professors may be not aware of potential benefits of AR applications in comparison to conventional learning tools. \\
This work considers two main research questions: 1.Which benefits are provided by an AR application in comparison to conventional learning tools? 2. How do those benefits differ regarding the different types of AR applications in educational environments? \\
Although recent studies have investigated the use of AR in educational environments \autocite {Wu.2013}\mulcit\autocite {Lee.2012} and a first approach to consolidate AR Benefits in educational environments has been made, \autocite [cf.][]{Radu.2014} more evidence on the educational values of AR is needed. Unfortunately, we were not able to replicate the approach by \cite{Radu.2014} in order to search for additional benefits because of missing information towards the applied methodology. In addition this approach does not consider the different types of AR applications in educational environments.\\
An overview of the benefits of AR in educational environments regarding the different types of AR applications would help teachers and professors to decide whether the implementation of AR is reasonable in certain educational scenarios.\\
\subsection{Objectives}
The main objective of this work is to identify benefits which can be provided by AR as a learning medium in educational environments in comparison to conventional learning tools. Besides, we want find out how these benefits differ regarding the different types of AR in educational environments. \\
To fulfill these objectives, we conducted a systematic literature review to identify and analyze relevant publications. In addition, we clustered relevant publications with regard to the applied type of AR on the basis of the 'Five Directions of AR in education' by \cite{Yuen.2011}.
\subsection{Structure}
The structure of this work is described in the following. The first chapter is called ‘Introduction’. It is divided into the subchapters ‘Problem Statement’, ‘Objectives’ and ‘Structure’. In this chapter we describe the reason why we decided to research for benefits of AR in educational environments. In addition, we point out the main objectives of our work.\\
In the second chapter, which is called ‘Augmented Reality in Educational Environments’ and is divided into the subchapters ‘Definitions of Augmented Reality’ and ‘Five Directions of Augmented Reality in Educational Environments’ we initially introduce our definition of AR and point out its meaning in today's education. Afterwards, we present the 'Five Directions' \autocite [cf.]{Yuen.2011} in which AR in educational environments can be categorized.\\
The third chapter is called ‘Systematic Literature Review’. It contains the subchapters ‘Data Collection’ and ‘Data Analysis’. In this chapter we describe our research approach.\\In the fourth chapter, which is called ‘Benefits of Augmented Reality in Educational Environments’ and is divided into the subchapters ‘Benefit Categorization’ and ‘Mapping of the Benefits to the Five Directions’, we present the main findings of our systematic literature review. Initially, we present the benefits we found during our literature analysis and provide groups of related benefits. Afterwards, we regard the relationship between the different directions of AR in educational environments and the benefits we identified.\\The fith chapter is called ‘Discussion’. In this chapter we discuss interesting aspects of our main findings before we mention the factors which limit our research.\\In the sixth chapter, which is called ‘Conclusion’, we provide the conclusion of our research.