\section{Research Approach}
We applied a two-step research approach, whereby we first conducted a systematic literature review to identify relevant publications before analysing the identified publications for the coding of benefits and directions. After coding, we grouped all found benefits.

\subsection{Systematic Literature Review}
For the identification of papers addressing Augmented Reality in educational environments, we applied a systematic online literature database search. We included databases which were specialised on more information systems centered papers, namely Institute of Electrical and Electronic Engineers (IEEE) Xplore Digital Library, ProQuest (ABI / INFORM), Association for Information Systems Electronic Library (AISel) and Association for Computing Machinery (ACM) Digital Library, as well as more general databases, namely EBSCO Host and ScienceDirect.\\
To find relevant papers, we searched within all databases with on the following attributes: title, abstract and author supplied keywords. Within these keywords we had three mandatory groups of keywords. Every article had to include the keyword "Augmented Reality". Additionally, every article needed to have at least one synonym for education and benefits. Namely we searched for "Educat*", "Learn*", "Teach*", "College" or "School" as synonyms for education and "Benefi*", "Advan*", "Improv*", "Enhanc*", "Driver*" or "Value*" as synonyms for benefits. To deal with the limitations of some databases, we had to split our query and conduct multiple queries on the database and merge them together by hand.\\
This database query resulted in a total of 600 articles. Those results then were checked against our include- and exclude-criteria, which are listed in \ref{tab:IncludeExcludeCriteria}, and were coded into one of the five directions. This process was performed by ourselves and each article was read by two of the authors.\\
After merging our results, a total of 63 articles remained. Those articles were then read again in full, each one by two of the authors and further checked against our include- and exclude-criteria. Also we refined our mappings into the different directions and selected the different benefits found in the articles.\\
Finally, 25 articles remained in compliance with our include- and exclude criteria.

\begin{table}[!htb]
    \center
    \begin{tabular}{p{17em} | p{17em}}
        \textbf{Include Criteria} & \textbf{Exclude Criteria} \\
        \hline
        %\cline{1-2}
        Empirical works & theoretical works, grey literature, dissertations \\
        A teaching problem is solved with the help of Augmented Reality or a teaching concept is improved by Augmented Reality & untried or untested technologies, concepts without empirical evidence \\
        Lists positive effects of the application of Augmented Reality & No control-group or control-scenario provided, no comparison without Augmented Reality applications \\
        Human learning & Machine learning \\
        English language & Other language \\
        Peer-reviewed & not peer-reviewed \\
    \end{tabular}
    \caption[Include- and Exclude-Criteria]{Include- and Exclude-Criteria}
    \label{tab:IncludeExcludeCriteria}
\end{table}

\subsection{Data Analysis}